\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-04-10 doc/USER_MANUAL/manual_SPECFEM3D.tex
added evolution of the code to the manual

This program is free software; you can redistribute it and/or modify
it under the terms of the GNU General Public License as published
by the Free Software Foundation (see Appendix \ref{cha:License}).

>>>>

This program is free software; you can redistribute it and/or modify
it under the terms of the GNU General Public License as published
by the Free Software Foundation (see Appendix \ref{cha:License}).\\

\textbf{\underline{Evolution of the code:}}\\

 MPI v. 2.0 `Sesame' (Spectral ElementS on Any MEsh), November 2010:
 Dimitri Komatitsch, Nicolas Le Goff, Roland Martin and Pieyre Le Loher, University of Pau, France,
 Jeroen Tromp and the Princeton group of developers, Princeton University, USA,
 and Emanuele Casarotti, INGV Roma, Italy:
  support for CUBIT meshes decomposed by SCOTCH, METIS or ZOLTAN;
  much faster solver using Michel Deville's inlined matrix products.\\

 MPI v. 1.4 Dimitri Komatitsch, University of Pau, Qinya Liu and others, Caltech, September 2006:
  better adjoint and kernel calculations, faster and better I/Os
  on very large systems, many small improvements and bug fixes.\\

 MPI v. 1.3 Dimitri Komatitsch, University of Pau, and Qinya Liu, Caltech, July 2005:
  serial version, regular mesh, adjoint and kernel calculations, ParaView support.\\

 MPI v. 1.2 Min Chen and Dimitri Komatitsch, Caltech, July 2004:
  full anisotropy, volume movie.\\

 MPI v. 1.1 Dimitri Komatitsch, Caltech, October 2002: Zhu's Moho map, scaling
  of $V_s$ with depth, Hauksson's regional model, attenuation, oceans, movies.\\

 MPI v. 1.0 Dimitri Komatitsch, Caltech, USA, May 2002: first MPI version based on global code.\\

 Dimitri Komatitsch, IPG Paris, France, December 1996: first 3-D solver for the CM-5 Connection Machine,
    parallelized on 128 processors using Connection Machine Fortran.\\
